How to select predictive models for decision-making or causal inference?

### 2023-12-15 how_to_select_causal_models.tex
move fig 1 in first pageé
iter

\onecolumn
\maketitle
\begin{abstract}
    \textbf{Objective:}
    As predictive models --\eg from machine learning-- give likely
    outcomes, they may be used to reason on the effect of an intervention, a
    causal-inference task. The increasing complexity of health data has opened
    the door to a plethora of models, but also the Pandora box of model
    selection: which of these models yield the most valid causal estimates?  In
    this paper, we study model selection procedures in practical settings:
    finite samples settings and without well-specification assumption.
    \textbf{Methods:}
    Elaborate risks build proxies of the causal error using ``nuisance''
    re-weighting to compute it on the observed data. But does computing these
    nuisance adds noise to model selection? Drawing from an extensive empirical
    study based on a simulation and three semi-simulated healthcare datasets
    based on real covariates, we compare different metrics for causal model
    selection.\\
    \textbf{Results:} Among all metrics the classical mean squared error (ie.
    factual $\mu\mathrm{-risk}$) is worse and re-weighting it with propensity score
    ($\mu\mathrm{-risk}_{IPW}$) does not bring much improvements. The
    $R\text{-risk}$, which includes a model of mean outcome and propensity
    scores, leads to the best performances.\\
    \textbf{Conclusions:} We outline a good causal model-selection procedure
    using the so-called $R\text{-risk}$; using flexible estimators to compute
    the nuisance models on the train set; and splitting out 10\% of the data to
    compute risks.
\end{abstract}
\keywords{Model Selection, Treatment Effect, G-formula, Observational Study, Machine Learning, }
\clearpage

>>>>

\onecolumn
\maketitle
\begin{abstract}
    \textbf{Objective:}
    As predictive models --\eg from machine learning-- give likely
    outcomes, they may be used to reason on the effect of an intervention, a
    causal-inference task. The increasing complexity of health data has opened
    the door to a plethora of models, but also the Pandora box of model
    selection: which of these models yield the most valid causal estimates? 
    We study such model selection procedures in practical settings:
    finite samples settings and without well-specification assumption.
    \textbf{Methods:}
    Elaborate risks build proxies of the causal error using ``nuisance''
    re-weighting to compute it on the observed data. But does computing these
    nuisance adds noise to model selection? Drawing from an extensive empirical
    study based on a simulation and three healthcare datasets
    based on real covariates, we compare different metrics for causal model
    selection.\\
    \textbf{Results:} Among all metrics the classical mean squared error (ie.
    factual $\mu\mathrm{-risk}$) is worse and re-weighting it with propensity score
    ($\mu\mathrm{-risk}_{IPW}$) does not bring much improvements. The
    $R\text{-risk}$, which includes a model of mean outcome and propensity
    scores, leads to the best performances.\\
    \textbf{Conclusions:} We outline a good causal model-selection procedure
    using the so-called $R\text{-risk}$; using flexible estimators to compute
    the nuisance models on the train set; and splitting out 10\% of the data to
    compute risks.
\end{abstract}
\keywords{Model Selection, Treatment Effect, G-formula, Observational Study, Machine Learning, }
\clearpage
